% Cover letter using letter.cls
\documentclass{letter}
\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{graphicx}
\usepackage[margin=0.5in, rmargin=1.in]{geometry}
\setlength{\textheight}{10in} % increase text height
\topmargin=-1.5in    % Make letterhead start about 1 inch from top of page
%\textheight=8in    % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\newcommand\mancenter[1]{\moveleft.5\hoffset\centerline{#1}}
\newcommand\boldline{\moveleft.0\hoffset\vbox{\hrule width\textwidth
    height 1pt}}
\newcommand\toedit[1]{\textcolor{red}{#1}} 
\begin{document}

 
\begin{letter}{Recruiting Manager\\
Oak Hill Advisors, L.P.\\
1114 Avenue of the Americas, 27th Floor\\
New York, NY 10036\\
}

\mancenter{\Large \bf{Benjamin A. Cook}} \mancenter{ 60 Garden St.~MS
  10, Cambridge, MA 02138 $\bullet$ (603) 313-2888}
\mancenter{  \href{mailto:bcook@cfa.harvard.edu}{bcook@cfa.harvard.edu} $\bullet$
  \href{http://www.cfa.harvard.edu/~bcook}{www.cfa.harvard.edu/$\sim$bcook}}
\boldline

\signature{\vspace{-0.3in}Ben Cook}                  % name for signature 
\longindentation=0pt                     % needed to get closing flush left
\let\raggedleft\raggedright              % needed to get date flush left

\opening{Dear Recruiting Manager,} 
 
\noindent I am writing to express my interest in a Summer 2018
quantitative internship with Oak Hill Advisors. I am a 4th-year PhD
candidate in astrophysics at Harvard, expect to complete my PhD in May
2019, and am eager for the chance to get an insider's view of working
in quantitative finance at Oak Hill. I recently spoke about the
opportunities available with Nathaniel Furmer at Harvard's Finance Career
Networking night on Thursday August 31st, and he recommended I reach
out personally to ask about internship opportunities for PhD
candidates. While Mr.~Furmer mentioned that Oak Hill has never had a PhD
candidate intern in the past, I believe my extensive training as an
independent researcher, my mindset for solving challenging problems
with statistical methods, and my experience using and teaching
GPU-acceleration for improving existing Python projects will make me a
great asset to your team this summer.

\noindent My skills and my interest in quantitative analysis both grew
from my early passion for astrophysics. During my undergraduate
studies at Princeton, my intellectual curiosity was centered on
questions surrounding the properties of super-massive black holes and
the nature of dark matter. But what excited me daily and kept me up
into the early-morning hours were challenges in computation and
analysis. I truly find nothing more thrilling than solving a
challenging problem through careful planning, clever statistical
analysis, and hard work.

\noindent Throughout my PhD program, I have solidified my foundations
as an independent researcher as well as expanded my computational
training through both course study and research applications. I have
taken graduate courses through the Computational Science and
Engineering program for five straight semesters, including
\textit{Stochastic Methods for Data Analysis, Inference and
  Optimization}, and \textit{Advanced Machine Learning}. I taught
myself the tools of GPU-acceleration with CUDA C and applied it to my
PhD thesis code to achieve a speed-up of over 16x compared to the
original Python. I have since become a participant in the NVIDIA
Developer and Educator program, have given several presentations on
the principles of GPU-acceleration, and was accepted to lead a
hands-on tutorial course at the upcoming .Astronomy 9 conference in
Cape Town, South Africa in November 2017.

\noindent I would be very excited for the opportunity to apply my
analytical skills and independence as a researcher to a summer
internship at Oak Hill. As a PhD candidate looking for eventual
employment in quantitative finance, I would like to prove myself
capable to apply my knowledge to problems in industry. I would
appreciate the opportunity to speak more about the possibility of an
internship for a PhD student, and look forward to hearing back from
you and learning more. Please feel free to contact me at (603)
313-2888 or bcook@cfa.harvard.edu.

Thank you for your time and consideration.

%Later, when applying for full-time positions, speak more about
%Leadership experience

\closing{Sincerely,}

%\encl{Resume}					% Enclosures

\end{letter}
\end{document}












