% Cover letter using letter.cls
\documentclass{letter}
\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{graphicx}
\usepackage[margin=0.5in, rmargin=1.in]{geometry}
\setlength{\textheight}{10in} % increase text height
\topmargin=-1.5in    % Make letterhead start about 1 inch from top of page
%\textheight=8in    % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\newcommand\mancenter[1]{\moveleft.5\hoffset\centerline{#1}}
\newcommand\boldline{\moveleft.0\hoffset\vbox{\hrule width\textwidth
    height 1pt}}
\newcommand\toedit[1]{\textcolor{red}{#1}} 
\begin{document}

 
\begin{letter}{Melissa Gontarz\\
Campus Recruiting\\
Wayfair\\
4 Copley Place, Floor 7\\
Boston, MA, 02116\\
}


\mancenter{\Large \bf{Benjamin A. Cook}} \mancenter{ 60 Garden St.~MS
  10, Cambridge, MA 02138 $\bullet$ (603) 313-2888}
\mancenter{  \href{mailto:bcook@cfa.harvard.edu}{bcook@cfa.harvard.edu} $\bullet$
  \href{http://www.cfa.harvard.edu/~bcook}{www.cfa.harvard.edu/$\sim$bcook}}
\boldline

\signature{\vspace{-0.3in}Ben Cook}                  % name for signature 
\longindentation=0pt                     % needed to get closing flush left
\let\raggedleft\raggedright              % needed to get date flush left

\opening{Dear Ms. Gontarz or whom it may concern,} 
 
\noindent I am writing to express my interest in the Summer 2018 Data
Science Intern position with Wayfair. I recently spoke at length with
you and Christina Teodorescu about the internships available at
Wayfair at Harvard's Campus Interview Program Fair on Friday September
8th. I am a 4th-year PhD candidate in astrophysics at Harvard with a
secondary field in Computational Science and Engineering, expect to
complete my PhD in May 2019, and am eager for the chance to get an
insider's view of working in data science at Wayfair this
summer. While you mentioned that PhD students have not previously been
part of Wayfair's summer internships, I believe my expertise in
statistical modeling, dealing with large datasets, and conducting
independent research will allow me to jump directly into a new or
ongoing data science project and make an immediate impact in the
company, especially in the Algorithms group.

\noindent My skills and my interest in data science both grew
from my early passion for astrophysics. During my undergraduate
studies at Princeton, my intellectual curiosity was centered on
questions surrounding the properties of super-massive black holes and
the nature of dark matter. But what excited me daily and kept me up
into the early-morning hours were challenges in computation and
analysis. I truly find nothing more thrilling than solving a
challenging problem through careful planning, clever statistical
analysis, and hard work.

\noindent Throughout my PhD program, I have solidified my foundations
as an independent researcher as well as expanded my computational
training through both course study and research applications. I have
taken graduate courses through the Computational Science and
Engineering program for five straight semesters, including
\textit{Stochastic Methods for Data Analysis, Inference and
  Optimization}, \textit{Data Science}, and \textit{Advanced Machine
  Learning}. I taught myself the tools of GPU-acceleration with CUDA C
and applied it to my PhD thesis code to achieve a speed-up of over 16x
compared to the original Python. I have since become a participant in
the NVIDIA Developer and Educator program, have given several
presentations on the principles of GPU-acceleration, and was accepted
to lead a hands-on tutorial course at the upcoming .Astronomy 9
conference in Cape Town, South Africa in November 2017.

\noindent I would be very excited for the opportunity to apply my
analytical skills and independence as a researcher to the summer data
science internship at Wayfair. As a PhD candidate looking for eventual
employment in data science, I would like to showcase my ability to
apply my knowledge to problems in industry, and believe Wayfair is
the ideal place to do so because of its ongoing growth and the
welcoming, collaborative atmosphere highlighted by the employees I
spoke with. I have also submitted an application through Harvard's
Crimson Careers portal, and would greatly appreciate the opportunity
to speak more in person. I look forward to hearing back from you and
learning more about the data science internship. Please feel free to
contact me at (603) 313-2888 or bcook@cfa.harvard.edu.

Thank you for your time and consideration.

%Later, when applying for full-time positions, speak more about
%Leadership experience

\closing{Sincerely,}

%\encl{Resume}					% Enclosures

\end{letter}
\end{document}












