% Cover letter using letter.cls
\documentclass{letter}
\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{graphicx}
\usepackage[margin=0.5in, rmargin=1.in]{geometry}
\setlength{\textheight}{10in} % increase text height
\topmargin=-1.5in    % Make letterhead start about 1 inch from top of page
%\textheight=8in    % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\newcommand\mancenter[1]{\moveleft.5\hoffset\centerline{#1}}
\newcommand\boldline{\moveleft.0\hoffset\vbox{\hrule width\textwidth
    height 1pt}}
\newcommand\toedit[1]{\textcolor{red}{#1}} 
\begin{document}

 
\begin{letter}{Hiring Manager\\
    Vatic Labs\\ New York, NY, 10017\\ }

\mancenter{\Large \bf{Benjamin A. Cook}} \mancenter{ 60 Garden St.~MS
  10, Cambridge, MA 02138 $\bullet$ (603) 313-2888}
\mancenter{  \href{mailto:bcook@cfa.harvard.edu}{bcook@cfa.harvard.edu} $\bullet$
  \href{http://www.cfa.harvard.edu/~bcook}{www.cfa.harvard.edu/$\sim$bcook}}
\boldline

\signature{\vspace{-0.3in}Ben Cook}                  % name for signature 
\longindentation=0pt                     % needed to get closing flush left
\let\raggedleft\raggedright              % needed to get date flush left

\opening{Dear Hiring Manager,} 
 
\noindent I am writing to express my interest in the Summer 2018
Quantitative Researcher Intern position with Vatic Labs. I am a
4th-year PhD candidate in astrophysics at Harvard with a secondary
field in Computational Science and Engineering. I expect to complete
my PhD in May 2019 and am eager for the chance to get an insider's
view of working in quantitative research at Vatic Labs this summer. I
believe my expertise in statistical modeling, dealing with large
datasets, and conducting independent research will allow me to jump
directly into a new or ongoing data science project and make an
immediate impact in the company.

\noindent My skills and interest in quantitative analysis both grew
from my early passion for astrophysics. During my undergraduate
studies at Princeton, my intellectual curiosity was centered on
questions surrounding the properties of super-massive black holes and
the nature of dark matter. But what excited me daily and kept me up
into the early-morning hours were challenges in computation and
analysis. I truly find nothing more thrilling than solving a
challenging problem through careful planning, clever statistical
analysis, and hard work.

\noindent Throughout my PhD program, I have solidified my foundations
as an independent researcher as well as expanded my computational
training through both course study and research applications. I have
taken graduate courses through the Computational Science and
Engineering program for five straight semesters, including
\textit{Stochastic Methods for Data Analysis, Inference and
  Optimization}, \textit{Data Science}, and \textit{Advanced Machine
  Learning}. I taught myself the tools of GPU-acceleration with CUDA C
and applied it to my PhD thesis code to achieve a speed-up of over 16x
compared to the original Python. I have since become a participant in
the NVIDIA Developer and Educator program, have given several
presentations on the principles of GPU-acceleration, and was accepted
to lead a hands-on tutorial course at the upcoming .Astronomy 9
conference in Cape Town, South Africa in November 2017.

\noindent I would be very excited for the opportunity to apply my
analytical skills and independence as a researcher to the summer
quantitative researcher internship at Vatic Labs. As a PhD candidate
looking for eventual employment in quantitative finance, I would like
to showcase my ability to apply my knowledge to problems in industry.
Please feel free to contact me at (603) 313-2888 or
bcook@cfa.harvard.edu.

Thank you for your time and consideration.

%Later, when applying for full-time positions, speak more about
%Leadership experience

\closing{Sincerely,}

%\encl{Resume}					% Enclosures

\end{letter}
\end{document}












