% Cover letter using letter.cls
\documentclass{letter}
\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{graphicx}
\usepackage[margin=0.5in, rmargin=1.in]{geometry}
\setlength{\textheight}{10in} % increase text height
\topmargin=-1.5in    % Make letterhead start about 1 inch from top of page
%\textheight=8in    % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\newcommand\mancenter[1]{\moveleft.5\hoffset\centerline{#1}}
\newcommand\boldline{\moveleft.0\hoffset\vbox{\hrule width\textwidth
    height 1pt}}
\newcommand\toedit[1]{\textcolor{red}{#1}} 
\begin{document}

 
\begin{letter}{Whom it may concern\\
Position \\
Institution\\
Address\\
City, State, ZIP\\
}


\mancenter{\Large \bf{Benjamin A. Cook}} \mancenter{ 60 Garden St.~MS
  10, Cambridge, MA 02138 $\bullet$ (603) 313-2888}
\mancenter{  \href{mailto:bcook@cfa.harvard.edu}{bcook@cfa.harvard.edu} $\bullet$
  \href{http://www.cfa.harvard.edu/~bcook}{www.cfa.harvard.edu/$\sim$bcook}}
\boldline

\signature{\vspace{-0.3in}Ben Cook}                  % name for signature 
\longindentation=0pt                     % needed to get closing flush left
\let\raggedleft\raggedright              % needed to get date flush left

\opening{To Whom It May Concern} 
 
\noindent I am writing to express my interest in \toedit{Quantitative
  Internship at Company Name} for the Summer of 2018. I recently
learned about \toedit{this program} when I met \toedit{Name} at the
\toedit{Career Fair at Harvard, on Thursday August 31st}, and look
forward to the chance to get an insider's view of \toedit{working in
  quantitative finance at Company} this summer. I am a 4th-year PhD
candidate in astrophysics at Harvard and expect to complete my PhD in
May 2019. I believe my extensive training as an independent
researcher, my mindset for solving challenging problems with
statistical methods, and my experience using and teaching
GPU-acceleration for improving existing Python projects will make me a
great fit for this internship.

\noindent My skills and my interest in \toedit{data analysis} both
grew from my early passion for astrophysics. During my undergraduate
studies at Princeton, my intellectual curiosity was centered on
questions surrounding the properties of super-massive black holes and
the nature of dark matter. But what excited me daily and kept me up
into the early-morning hours were challenges in computation and
analysis. To this day I remember the feeling of elation I felt when I
located the last bug from my Junior Thesis code modeling the
time-series photometry of the asteroid Iris. It was nearly 4AM, one
morning in early January 2012, and when my monitor finally displayed a
sine-curve showing a rotation period of 7.14($\pm0.012$) hours, I
couldn't help but get up and dance around the empty computer lab. I
truly find nothing more thrilling than solving a challenging problem
through careful planning, clever statistical analysis, and hard work.

\noindent Throughout my PhD program, I have solidified my foundations
as an independent researcher as well as expanded my computational
training through both course study and research applications. I have
taken graduate courses through the Computational Science and
Engineering program for five straight semesters, including
\textit{Stochastic Methods for Data Analysis, Inference and
  Optimization}, and \textit{Advanced Machine Learning}. I taught
myself the tools of GPU-acceleration with CUDA C and applied it to my
PhD thesis code to achieve a speed-up of over 16x compared to the
original Python. I have since become a participant in the NVIDIA
Developer and Educator program, have given several presentations on
the principles of GPU-acceleration, and was accepted to lead a
hands-on tutorial course at the upcoming .Astronomy 9 conference in
Cape Town, South Africa in November 2017.

\noindent I would be very excited for the opportunity to apply my
analytical skills and independence as a researcher to an internship at
\toedit{Company Name}. As a PhD candidate looking for eventual
employment in \toedit{finance, data science, etc.}, I would like to
prove myself capable to apply my knowledge to problems in industry,
and believe \toedit{Company Name} is the ideal place to do so
\toedit{because of various reasons}. I look forward to hearing back
from you and learning more \toedit{about what opportunities are
  available for someone in my position}.

Thank you for your time and consideration.

%Later, when applying for full-time positions, speak more about
%Leadership experience

\closing{Sincerely,}
%\encl{}					% Enclosures

\end{letter}
\end{document}












