% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{graphicx}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\topmargin=-0.2in % start text higher on the page
\setlength{\textheight}{9.5in} % increase text height to fit resume on 1 page
\newcommand\mancenter[1]{\moveleft.5\hoffset\centerline{#1}}

\begin{document}  
\moveleft.5\hoffset\centerline{\huge \bf{Benjamin A. Cook} -
  \textit{Extracurricular R\'esum\'e}} \mancenter{\large Department of
  Astrophysical Sciences, Princeton University} \mancenter{\large 4
  Ivy Lane, Princeton, NJ 08544}
\mancenter{\large\tt\href{mailto:bacook@princeton.edu}{bacook@princeton.edu}}
\begin{resume}                        
 
%\section{OBJECTIVE}      PhD Student in Cosmology and Astrophysics 

\section{TEACHING}
\begin{itemize}
\item Teaching Assistant to Prof.~Neta Bahcall (Spring 2013)
\item[] \textit{AST 204: Topics in Modern Astronomy}
\item Teaching Assistant to Prof.~G\'asp\'ar Bakos (Fall 2012)
\item[] \textit{AST 205: Planets in the Universe}
\end{itemize}

\section{EMPLOYMENT and LEADERSHIP}
\begin{itemize} 
                   \item President of Princeton Society of Physics
                     Students: Spring 2012 - Present
                   	\item[] \textit{Organized colloquia and group
                          activities; authored club constitution}
                   \item Princeton University Ticketing Manager: Fall
                     2012 - Present
                    \item[] \textit{Trained and supervised student
                      employees in daily ticketing office operations}
                      \item Princeton University Ticketing Associate:
                        Fall 2010 - Fall 2012
                        \item[] \textit{Responsible for customer
                          service relations, on-site operations, and
                          phone sales}
                   \end{itemize}

\section{OUTREACH}
                  \begin{itemize}
                  \item Volunteer presenter at \textit{Mars and
                    Beyond} exhibit, Boston Museum of Science (August
                    2013).
                  \item Volunteer host for Peyton Observatory public
                    observing nights (2012-present).
                  \item Volunteer proctor for Princeton University
                    Mathematics Competition (PUMaC, 2010-present).
                  \item Peer Major-Choices Adviser (2013-present).
                  \item Campus Tour Guide (2011-2012).
                  \end{itemize} 

\section{PERSONAL and ATHLETIC}
\begin{itemize}
\item Scuba Diving
\item[] \textit{Advanced Open Water, Equipment Specialist, and Wreck Diving certified. Over 75 logged dives since 2004.}
\item Baseball
\item[] \textit{Pitcher and First Baseman. Member of Babe Ruth and Senior Babe Ruth leagues until Sophomore year.}
\end{itemize}
\end{resume} 
\end{document}

