% Cover letter using letter.cls
\documentclass{letter}
\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{graphicx}
\usepackage[margin=0.5in, rmargin=1.in]{geometry}
\setlength{\textheight}{10in} % increase text height
\topmargin=-1.5in    % Make letterhead start about 1 inch from top of page
%\textheight=8in    % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\newcommand\mancenter[1]{\moveleft.5\hoffset\centerline{#1}}
\newcommand\boldline{\moveleft.0\hoffset\vbox{\hrule width\textwidth
    height 1pt}}
\newcommand\toedit[1]{\textcolor{red}{#1}} 
\begin{document}

 
\begin{letter}{}


\mancenter{\Large \bf{Benjamin A. Cook}} \mancenter{ 60 Garden St.~MS
  10, Cambridge, MA 02138 $\bullet$ (603) 313-2888}
\mancenter{  \href{mailto:bcook@cfa.harvard.edu}{bcook@cfa.harvard.edu} $\bullet$
  \href{http://www.cfa.harvard.edu/~bcook}{www.cfa.harvard.edu/$\sim$bcook}}
\boldline

\signature{\vspace{-0.3in}Ben Cook}                  % name for signature 
\longindentation=0pt                     % needed to get closing flush left
\let\raggedleft\raggedright              % needed to get date flush left

\opening{To Whom It May Concern,} 

I would like to express my interest in joining your quantitative research team,
which was brought to my attention by Mr.~Cambi. I am an Astrophysics PhD
candidate at Harvard University, where I have been actively engaged in research
and coursework in high-performance computation and machine learning. My thesis
research focuses on developing a forward-modeling analysis pipeline for
inferring the properties of galaxies. Through this project I have gained
significant experience with GPU-acceleration, improving the simulation time by
a factor of $34\times$, and with modern cloud computing. I also recently
completed a Quantitative Analysis internship at D.E.~Shaw. I received a very
positive letter of recommendation from my manager for my work in studying the
accuracy and interpretability of Neural Networks for predicting mortgage
default rates.

Throughout my academic career, I have proven myself to be a talented
programmer, creative problem solver, and quick to learn new tools and fields. I
believe I could be a beneficial addition to your new research team, and I hope
to speak further with you about this opportunity.

Thank you for your time and consideration.

%Later, when applying for full-time positions, speak more about
%Leadership experience

\closing{Sincerely,}

%\encl{Resume}					% Enclosures

\end{letter}
\end{document}












