% Cover letter using letter.cls
\documentclass{letter}
\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{graphicx}
\usepackage[margin=0.5in, rmargin=1.in]{geometry}
\setlength{\textheight}{10in} % increase text height
\topmargin=-1.5in    % Make letterhead start about 1 inch from top of page
%\textheight=8in    % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\newcommand\mancenter[1]{\moveleft.5\hoffset\centerline{#1}}
\newcommand\boldline{\moveleft.0\hoffset\vbox{\hrule width\textwidth
    height 1pt}}
\newcommand\toedit[1]{\textcolor{red}{#1}} 
\begin{document}

 
\begin{letter}{Hiring Manager\\
    Barclays Investment Bank\\ 745 Seventh Ave\\ New York, NY 10019\\ }


\mancenter{\Large \bf{Benjamin A. Cook}} \mancenter{ 60 Garden St.~MS
  10, Cambridge, MA 02138 $\bullet$ (603) 313-2888}
\mancenter{  \href{mailto:bcook@cfa.harvard.edu}{bcook@cfa.harvard.edu} $\bullet$
  \href{http://www.cfa.harvard.edu/~bcook}{www.cfa.harvard.edu/$\sim$bcook}}
\boldline

\signature{\vspace{-0.3in}Ben Cook}                  % name for signature 
\longindentation=0pt                     % needed to get closing flush left
\let\raggedleft\raggedright              % needed to get date flush left

\opening{Dear Hiring Manager,}

\noindent I am writing to inquire about the Quantitative Analyst position 
at Barclays. I am a 5th-year PhD candidate in astrophysics at Harvard, and
will be receiving my degree in May with a secondary field certification in
Computational Science and Engineering. I believe my demonstrated ability to
solve challenging problems through computation and mathematics and my strong
communication and leadership skills would make me an excellent addition to your
research team.

\noindent Throughout my research career, I have consistently shown a
proficiency for self-guided, independent research and have taken significant
steps to expand my expertise in high-performance computing and machine
learning. My thesis research focuses on developing a Python package to simulate
images of galaxies as seen by the Hubble Space Telescope and applying Bayesian
inference to measure the properties of galaxies for which no other techniques
can be used. My most significant contributions include applying GPU
computing to accelerate the modeling procedure by a factor of more than
$30\times$, and using Amazon Web Services to run dozens of simultaneous
simulations via the cloud.

\noindent I've also demonstrated my ability to apply my programming and machine
learning skills in an industry setting through my quantitative analysis
internship at D.E.~Shaw. My research project in the Asset-Backed Securities
group involved developing and training TensorFlow neural networks to predict
prepayment rates of GNMA mortgages, with the eventual goal of application to
pricing Mortgage-Backed Securities. In addition to developing and fine-tuning
the models, I also presented an extensive report and presentation on their
accuracy, comparisons to existing techniques, and methods for interpreting
their predictions and identifying the most important features and feature
interactions. I received a positive performance review and letter of
recommendation from my manager, available upon request.

\noindent I've had numerous opportunities to showcase my communication skills
and talent for leadership. I serve as the Treasurer for a national
non-profit, a series of science communication workshops for graduate students
called ComSciCon, and was the chair of National Workshop organizing team for 3
years. I've twice been awarded the Certificate of Teaching Excellence from
Harvard's Bok Center, and volunteer each summer as an instructor and mentor to
underrepresented astrophysics students of color at Harvard's Banneker
Institute. I've also become a resource for other researchers in my community
looking to learn about HPC techniques, having hosted several workshops and
tutorials on GPU programming, Docker containers, and cloud computing.

\noindent While I've treasured my time in academia, I'm extremely excited to
transition to a career in quantitative finance. I found my internship at
D.E.~Shaw exhilarating, and I look forward to applying my talent for creative,
computational problem solving to an industry where new challenges arise every
day. I have an excellent combination of mathematical and programming
expertise, strong communication skills, and the proven ability to work
independently and find unique solutions to challenging problems. I believe I
would be a significant addition to the team at Barlays, and I look forward to
speaking with your further about the opportunity.

Thank you for your time and consideration.

\closing{Sincerely,}

\end{letter}
\end{document}












